---
title: "Reproducible Analysis for CASA0005 Final Project"
author: "Yichen Tian"
date: "27/12/2020"
output:
  html_document:
    theme: yeti
    smart: true
    highlight: textmate
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load libraries

```{r echo=TRUE}
library(sp)
library(spatstat)
library(here)
library(rgeos)
library(maptools)
library(GISTools)
library(tmap)
library(sf)
library(geojson)
library(geojsonio)
library(tmaptools)
library(tidyverse)
library(fs)
library(stringr)
library(tigris)
library(raster)
library(grid)
library(ggplot2)
library(spdep)
library(magrittr)
library(RColorBrewer)
library(viridis)
library(fpc)
library(dbscan)
library(OpenStreetMap)
library(factoextra)
library(tidymodels)
library(caret)
```

# Preliminary analysis:
## Descrptive Analysis - Distribution of data

We slice the data to four periods of time and plot them to see the distribution of their densities. 

NOTE: Tweets data here is a random mock dataset, and it is only for demonstration purposes. 

```{r}
####important###
# if you have london MSOA shp file 
# please dont run the following lines
# as it will download the zip file here at your wd
# and navigate to the shp we want
# instead run the commented out lines that begins with msoabounds
temp <- tempfile()
temp2 <- tempfile()
download.file("https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip",temp)
unzip(zipfile = temp, exdir = temp2)

msoabounds<-st_read(file.path(temp2,"statistical-gis-boundaries-london","ESRI","MSOA_2011_London_gen_MHW.shp" ))%>%
  st_transform(., 27700)
unlink(c(temp, temp2))


#msoabounds <- st_read(here::here("../../bigData", 
#                               "statistical-gis-boundaries-london",
#                                "ESRI",
#                                "MSOA_2011_London_gen_MHW.shp"))%>%
#  st_transform(., 27700)
                      
pop <- read_csv('https://github.com/Tiana125/2020GIS_Final/raw/main/reproducible%20analysis/land-area-population-density-lsoa11-msoa11.csv')

msoapop <- geo_join(msoabounds,pop,'MSOA11CD','MSOA11CD')

census <- read_csv("https://github.com/Tiana125/2020GIS_Final/raw/main/RMD/msoadata.csv")
msoacensus <- geo_join(msoabounds,census,'MSOA11CD','MSOA11CD')

msoacensus <- msoacensus%>%
  mutate(workpop_density=working_pop/msoapop$population)

tweet1222 <- st_read('https://github.com/Tiana125/2020GIS_Final/raw/main/1222data_mock.csv') %>%
  st_as_sf(., coords = c("long", "lat"), 
           crs = 4326)%>%
  st_transform(., 27700)

# the following code is used for the real data
tweet1222 <- tweet1222[msoabounds,]
tweet1222_latepeak <- tweet1222 %>% slice(1:152,1792:1991)
tweet1222_home <- tweet1222 %>% slice(153:849)
tweet1222_mornpeak <- tweet1222 %>% slice(850:1078)
tweet1222_work <- tweet1222 %>% slice(1079:1792)

dist_1222tw <- data.frame(c('morning peak', 'workplace', 'evening peak', 'home'),
                       c(nrow(tweet1222_mornpeak), nrow(tweet1222_work), 
                         nrow(tweet1222_latepeak), nrow(tweet1222_home)))
colnames(dist_1222tw) <-c('period', 'number_of_tweets')
dist_1222tw$timespan <- c(3,6.5,3,11.5)
dist_1222tw %<>% mutate(density=number_of_tweets/timespan)

dist_1222tw$x <- c(1.5,6.5,11.5,19)
x_tick <- c(0, length(dist_1222tw$x)) + 0.5
len <- length(x_tick)
ggplot(dist_1222tw, aes(x = x, y = density,width=timespan)) + 
#  ggtitle("Distribution of number of geo-tagged tweets #\nsent per hour") +
  xlab("Time") + ylab("Density of tweets") +
  geom_col(position = "dodge") +
  ylim(0,150) +
  geom_text(data=dist_1222tw, 
            aes(label=round(density)), 
            position = position_dodge(width=dist_1222tw$timespan),
            vjust=-0.3, size=5) +
  scale_x_continuous(breaks = c(0,3.15,9.9,13.15,24.85),
                     labels = c('0'='6:30','3.15'='9:30',
                                 '9.9'='16:00', '13.15'='19:00', '24.85'='6:30\nnext day')) 
```


```{r}
tmplot_tweets <- function(whichtweet){
  tweetineachmsoa <- msoapop%>%
    st_join(whichtweet)%>%
    add_count(MSOA11NM)%>%
    #then density of the points per ward
    mutate(density=n/population)%>%
    #select density and some other variables 
    dplyr::select(density, MSOA11NM, MSOA11CD, n)
  
  tweetineachmsoa<- tweetineachmsoa %>%                    
    group_by(MSOA11CD) %>%         
    summarise(density = first(density),
              wardname= first(MSOA11NM),
              tweetcount= first(n))
  
  t <- tm_shape(tweetineachmsoa) +
    tm_borders(lwd=.1)+
    tm_polygons("density",
                style="jenks",
                palette=c('#ffffcc', '#a1dab4', '#41b6c4', '#2c7fb8', '#253494'),
                midpoint=NA,
                popup.vars=c("wardname", "density"),
                title="Tweet Density") 
    
}

tmap_all_1222 <- tmplot_tweets(tweet1222)
tmap_home_1222 <- tmplot_tweets(tweet1222_home)
tmap_work_1222 <- tmplot_tweets(tweet1222_work)
tmap_mornpeak_1222 <- tmplot_tweets(tweet1222_mornpeak)
tmap_latepeak_1222 <- tmplot_tweets(tweet1222_latepeak)

tm_shape(msoabounds) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(tweet1222) +
  tm_dots(col = "blue")

```




```{r}

tweetineachmsoa <- msoapop%>%
  st_join(tweet1222)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n)

tweetineachmsoa<- tweetineachmsoa %>%                    
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))

tmap_mode("plot")
tm_work <- tm_shape(msoacensus) + 
  tm_borders(lwd=.1)+
  tm_polygons("workpop_density",style = "jenks") +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("density of people in work", position=c(0,0.85), size=1)

tm_res <- tm_shape(msoacensus) + 
  tm_polygons("resident_num",style = "jenks") +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("(a2)", position=c(0,0.85), size=1.5)

tm_tweet <- tmap_all_1222 +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("tweet density across all users", position=c(0,0.85), size=1)

tmap_home_1222 <- tmap_home_1222 +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("tweet density from 19:00-6:00", position=c(0,0.85), size=1)

    #main.title= 'Density of tweets sent from home', 
            #main.title.position = c('center', 'top'), frame=FALSE,
            #legend.hist.width = 0.6,legend.hist.height = .3,
            #legend.outside.position = "right", legend.outside.size = 0.3,
            #legend.outside = TRUE)
#  tm_credits("()", position=c(0,0), size=1)

tmap_work_1222 <- tmap_work_1222 +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_borders(col="grey",lwd=.1)+
  tm_credits("tweet density from 9:30-16:00", position=c(0,0.85), size=1)

tmap_mornpeak_1222 <- tmap_mornpeak_1222 +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("tweet density during 6:30-9:30", position=c(0,0.85), size=1)

tmap_latepeak_1222 <- tmap_latepeak_1222 +
  tm_layout(frame=FALSE,legend.outside = TRUE)+
  tm_credits("tweet density during 16:00-19:00", position=c(0,0.85), size=1)

alltweetsmap=tmap_arrange(tm_tweet, tmap_mornpeak_1222,tmap_work_1222,
                          tmap_latepeak_1222,
                          tmap_home_1222, tm_work, ncol=2)
alltweetsmap

```


```{r}
tweetineachmsoa_work <- msoapop%>%
  st_join(tweet1222_work)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))

tweetineachmsoa_home <- msoapop%>%
  st_join(tweet1222_home)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))


tweetineachmsoa_latepeak <- msoapop%>%
  st_join(tweet1222_latepeak)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))


tweetineachmsoa_mornpeak <- msoapop%>%
  st_join(tweet1222_mornpeak)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))


```

# Spatial Autocorrelation Statistics

```{r morans I on tweets}
coordsmsoa <- msoabounds%>%
  st_centroid()%>%
  st_geometry()
  
plot(coordsmsoa,axes=TRUE)

msoa_nb <- msoabounds %>%
  poly2nb(., queen=TRUE,snap=1)

#plot them
plot(msoa_nb, st_geometry(msoabounds), col="red")
#add a map underneath
plot(tweetineachmsoa$geometry, border = "grey",add=T)

Lmsoa.lw <- msoa_nb %>%
  nb2listw(., style="C")

I_Lmsoa_Global_Density <- tweetineachmsoa %>%
  pull(density) %>%
  as.vector()%>%
  moran.test(., Lmsoa.lw)

I_Lmsoa_Global_Density 

C_Lmsoa_Global_Density <- tweetineachmsoa %>%
  pull(density) %>%
  as.vector()%>%
  geary.test(., Lmsoa.lw)

C_Lmsoa_Global_Density 

G_Lmsoa_Global_Density <- tweetineachmsoa %>%
  pull(density) %>%
  as.vector()%>%
  globalG.test(., Lmsoa.lw) 

G_Lmsoa_Global_Density #greater, high values are tending to cluster.

#use the localmoran function to generate I for each ward in the city
I_Lmsoa_Local_count <- tweetineachmsoa %>%
  pull(tweetcount) %>%
  as.vector()%>%
  localmoran(., Lmsoa.lw)%>%
  as_tibble()

I_Lmsoa_Local_Density <- tweetineachmsoa %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Lmsoa.lw)%>%
  as_tibble()

#what does the output (the localMoran object) look like?
slice_head(I_Lmsoa_Local_Density, n=5)

tweetineachmsoa <- tweetineachmsoa %>%
  mutate(tweet_count_I = as.numeric(I_Lmsoa_Local_count$Ii))%>%
  mutate(tweet_count_Iz =as.numeric(I_Lmsoa_Local_count$Z.Ii))%>%
  mutate(density_I =as.numeric(I_Lmsoa_Local_Density$Ii))%>%
  mutate(density_Iz =as.numeric(I_Lmsoa_Local_Density$Z.Ii))

breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
MoranColours<- rev(brewer.pal(8, "RdGy"))

tmap_mode('view')
tm_shape(tweetineachmsoa) +
    tm_polygons("tweet_count_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, Tweets in London")

Gi_Lmsoa_Local_Density <- tweetineachmsoa %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Lmsoa.lw)

tweetineachmsoa <- tweetineachmsoa %>%
  mutate(density_G = as.numeric(Gi_Lmsoa_Local_Density))

GIColours<- rev(brewer.pal(8, "RdBu"))

#now plot on an interactive map
tm_shape(tweetineachmsoa) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, Tweets in London")


```



```{r morans I working_pop}

I_Lmsoa_Global_Density_workpop <- msoacensus %>%
  pull(workpop_density) %>%
  as.vector()%>%
  moran.test(., Lmsoa.lw)

I_Lmsoa_Global_Density_workpop #greater, 0.4195210731   

C_Lmsoa_Global_Density_workpop <- msoacensus %>%
  pull(workpop_density) %>%
  as.vector()%>%
  geary.test(., Lmsoa.lw)

C_Lmsoa_Global_Density_workpop # 1.06788251, negative spatial autocorrelation or dissimilar values clustering, NO

G_Lmsoa_Global_Density_workpop <- msoacensus %>%
  pull(workpop_density) %>%
  as.vector()%>%
  globalG.test(., Lmsoa.lw) 

G_Lmsoa_Global_Density_workpop #greater, high values are tending to cluster.

#use the localmoran function to generate I for each ward in the city
I_Lmsoa_Local_count_workpop <- msoacensus %>%
  pull(working_pop) %>%
  as.vector()%>%
  localmoran(., Lmsoa.lw)%>%
  as_tibble()

I_Lmsoa_Local_Density_workpop <- msoacensus %>%
  pull(workpop_density) %>%
  as.vector()%>%
  localmoran(., Lmsoa.lw)%>%
  as_tibble()

#what does the output (the localMoran object) look like?
slice_head(I_Lmsoa_Local_Density_workpop, n=5)

msoacensus <- msoacensus %>%
  mutate(workpop_count_I_workpop = as.numeric(I_Lmsoa_Local_count_workpop$Ii))%>%
  mutate(workpop_count_Iz =as.numeric(I_Lmsoa_Local_count_workpop$Z.Ii))%>%
  mutate(workpop_density_I =as.numeric(I_Lmsoa_Local_Density_workpop$Ii))%>%
  mutate(workpop_density_Iz =as.numeric(I_Lmsoa_Local_Density_workpop$Z.Ii))

breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
MoranColours<- rev(brewer.pal(8, "RdGy"))

tmap_mode('view')
tm_shape(msoacensus) +
    tm_polygons("workpop_count_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, working population in London")

Gi_Lmsoa_Local_Density_workpop <- msoacensus %>%
  pull(workpop_density) %>%
  as.vector()%>%
  localG(., Lmsoa.lw)

msoacensus <- msoacensus %>%
  mutate(workpop_density_G = as.numeric(Gi_Lmsoa_Local_Density_workpop))

GIColours<- rev(brewer.pal(8, "RdBu"))

#now plot on an interactive map
tm_shape(msoacensus) +
    tm_polygons("workpop_density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, working population in London")
```





```{r}
msoatweetsSub<- tweet1222 %>%
  as(., 'Spatial')

window <- as.owin(msoabounds)

msoatweetsSub.ppp <- ppp(x=msoatweetsSub@coords[,1],
                          y=msoatweetsSub@coords[,2],
                          window=window)
msoatweetsSub.ppp %>%
  plot(.,pch=16,cex=0.5, lwd=.1,
       main="tweets in london")
msoatweetsSub.ppp %>%
  density(., sigma=500) %>%
  plot()

K <- msoatweetsSub.ppp %>%
  Kest(., correction="border") %>%
  plot()

```



```{r}
msoatweetsSubpoints <- msoatweetsSub %>%
  coordinates(.)%>%
  as.data.frame()

msoatweetsSubpointsmap <- ggplot(msoatweetsSubpoints, 
                      aes(x=coords.x1,y=coords.x2))+
  geom_point()+
  coord_equal()

msoatweetsSubpointsmap
msoatweetsSubpointsmap+stat_density2d(aes(fill = ..level..), geom="polygon")

msoatweetsSubpointsmap<-ggplot(msoatweetsSubpoints, 
                    aes(x=coords.x1,y=coords.x2))+
  stat_bin2d(bins=10)

msoatweetsSubpointsmap

```

Below shows kmeans clustering, numbers of clusters chose arbitrarily. (Results won't be included in paper. )

```{r kmeans}
kmeanstweets <- kmeans(msoatweetsSubpoints, centers = 5)
fviz_cluster(kmeanstweets, data = msoatweetsSubpoints)

```

# Removing outliers using DBSCAN and OPTICS


```{r}
# Split the data:
indxTrain <- createDataPartition(y = msoatweetsSubpoints$coords.x2,
                                 p = 0.75,list = FALSE)
training <- msoatweetsSubpoints[indxTrain,]
testing <- msoatweetsSubpoints[-indxTrain,]

# Run k-NN:
set.seed(400)
ctrl <- trainControl(method="repeatedcv", number=10, repeats=5)
knnFit <- train(coords.x1 ~ ., data = training, method = "knn", trControl = ctrl, preProcess = c("center","scale"),tuneLength = 20)
knnFit

#Use plots to see optimal number of clusters:
plot(knnFit,xlim=c(1,50))
```




All tweets in London, DBSCAN analysis. 
```{r DBSCAN all tweets}
msoatweetsSubpoints <- msoatweetsSub %>%
  coordinates(.)%>%
  as.data.frame()

db <- msoatweetsSubpoints %>%
  fpc::dbscan(.,eps = 1600, MinPts = 7)

#now plot the results
plot(db, msoatweetsSubpoints, main = "DBSCAN Output", frame = F)
plot(msoabounds$geometry, add=TRUE)

kNNdistplot(msoatweetsSubpoints,k=5)+
abline(h=1600, col = "red", lty=2)
msoatweetsSubpoints<- msoatweetsSubpoints %>%
  mutate(dbcluster=db$cluster)

chulls <- msoatweetsSubpoints %>%
  group_by(dbcluster) %>%
  dplyr::mutate(hull = 1:n(),
                hull = factor(hull, chull(coords.x1, coords.x2)))%>%
  arrange(hull)

chulls <- chulls %>%
  filter(dbcluster >=1)

dbplot <- ggplot(data=msoatweetsSubpoints, 
                 aes(coords.x1,coords.x2, colour=dbcluster, fill=dbcluster)) 
#add the points in
dbplot <- dbplot + geom_point()
#now the convex hulls
dbplot <- dbplot + geom_polygon(data = chulls, 
                                aes(coords.x1,coords.x2, group=dbcluster), 
                                alpha = 0.5) 
#now plot, setting the coordinates to scale correctly and as a black and white plot 
dbplot + theme_bw() + coord_equal()

msoabb <- msoabounds %>%
  st_transform(., 4326)%>%
  st_bbox()

basemap <- OpenStreetMap::openmap(c(51.28,-0.489),c(51.686,0.236),
                         zoom=NULL,
                         "stamen-toner")

  # convert the basemap to British National Grid
basemap_bng <- openproj(basemap, projection="+init=epsg:27700")

autoplot.OpenStreetMap(basemap_bng) + 
  geom_point(data=msoatweetsSubpoints, 
             aes(coords.x1,coords.x2, 
                 colour=dbcluster, 
                 fill=dbcluster)) + 
  geom_polygon(data = chulls, 
               aes(coords.x1,coords.x2, 
                   group=dbcluster,
                   fill=dbcluster), 
               alpha = 0.5)  

tweets_noisefree <- msoatweetsSubpoints[!(msoatweetsSubpoints$dbcluster==0),]

ggplot(data=tweets_noisefree, 
       aes(coords.x1,coords.x2, colour=dbcluster, fill=dbcluster)) +
  geom_point()

tweets_noisefree_xy <- tweets_noisefree %>%
  st_as_sf(coords = c("coords.x1", "coords.x2"), crs = 27700)

tm_shape(msoabounds) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(tweets_noisefree_xy) +
  tm_dots(col = "blue")

crs(tweets_noisefree_xy)
tweetineachmsoa_work_noisefree <- msoapop%>%
  st_join(tweets_noisefree_xy)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))

t_noisefree <- tm_shape(tweetineachmsoa_work_noisefree) +
    tm_polygons("density",
                style="jenks",legend.hist = TRUE,
                palette=c('#ffffcc', '#a1dab4', '#41b6c4', '#2c7fb8', '#253494'),
                midpoint=NA,
                popup.vars=c("wardname", "density"),
                title="Tweet Density")

```


```{r}
#tweetineachmsoa <- msoapop%>%
#    st_join(whichtweet)%>%
#    add_count(MSOA11NM)%>%
    #then density of the points per ward
#    mutate(density=n/population)%>%
    #select density and some other variables 
#    dplyr::select(density, MSOA11NM, MSOA11CD, n)

msoatweetsSubpoints <- msoatweetsSubpoints%>%
  add_count(dbcluster)%>%
  mutate(numincluster=n)%>%
  dplyr::select(coords.x1,coords.x2,dbcluster,numincluster)

max(msoatweetsSubpoints$dbcluster)
```




```{r all tweets OPTICS}
opt <- msoatweetsSubpoints %>%
  dbscan::optics(.,eps=1400, minPts = 7)

plot(opt)

reach <- as.reachability(opt)
#Avg minimum reachability distance: 359.4764

opt <- extractDBSCAN(opt, eps_cl = 360)
plot(opt)


hullplot(msoatweetsSubpoints, opt, frame = F)
plot(msoabounds$geometry, add=TRUE)

msoatweetsSubpoints<- msoatweetsSubpoints %>%
  dplyr::mutate(optcluster=opt$cluster)

optchulls <- msoatweetsSubpoints %>%
  group_by(optcluster) %>%
  dplyr::mutate(hull = 1:n(),
                hull = factor(hull, chull(coords.x1, coords.x2)))%>%
  arrange(hull)

optchulls <- optchulls %>%
  filter(optcluster >=1)

optplot <- ggplot(data=msoatweetsSubpoints, 
                 aes(coords.x1,coords.x2, colour=optcluster, fill=optcluster))


#add the points in
#optplot <- optplot + geom_point()
#now the convex hulls
optplot <- optplot + geom_polygon(data = optchulls, 
                                aes(coords.x1,coords.x2, group=dbcluster), 
                                alpha = 0.5) 

#now plot, setting the coordinates to scale correctly and as a black and white plot 

optplot +  theme_bw() + coord_equal()


autoplot.OpenStreetMap(basemap_bng) + 
  geom_point(data=msoatweetsSubpoints, 
             aes(coords.x1,coords.x2, 
                 colour=optcluster, 
                 fill=optcluster)) + 
  geom_polygon(data = optchulls, 
               aes(coords.x1,coords.x2, 
                   group=optcluster,
                   fill=optcluster), 
               alpha = 0.5)  

msoatweetsSubpoints <- msoatweetsSubpoints%>%
  add_count(optcluster)%>%
  mutate(numinoptcluster=n)%>%
  dplyr::select(coords.x1,coords.x2,dbcluster,numincluster,optcluster, numinoptcluster)

tweets_noisefree_opt <- msoatweetsSubpoints[!(msoatweetsSubpoints$optcluster==0),]

tweets_noisefree_opt_xy <- tweets_noisefree_opt %>%
  st_as_sf(coords = c("coords.x1", "coords.x2"), crs = 27700)
tmap_mode('plot')
tm_shape(msoabounds) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(tweets_noisefree_xy) +
  tm_dots(col = "blue")

tweetineachmsoa_work_noisefree_opt <- msoapop%>%
  st_join(tweets_noisefree_xy)%>%
  add_count(MSOA11NM)%>%
  #calculate area
  #then density of the points per ward
  mutate(density=n/population)%>%
  #select density and some other variables 
  dplyr::select(density, MSOA11NM, MSOA11CD, n) %>%
  group_by(MSOA11CD) %>%         
  summarise(density = first(density),
            wardname= first(MSOA11NM),
            tweetcount= first(n))

```

# Plotting and Residuals...

```{r all tweets regression}
#plottw <- tweets_noisefree_opt%>%
#  dplyr::select('MSOA11CD', 'density') 
plottw <- tweetineachmsoa_work_noisefree_opt%>%
  dplyr::select('MSOA11CD', 'density') 

plotcen <- msoacensus%>%
  dplyr::select('MSOA11CD', 'workpop_density') 

plottog <-  inner_join(plottw %>% as.data.frame(), plotcen %>% as.data.frame(), by = "MSOA11CD")
#plottog <- plottog %>% slice(2:983)
                              
hist(plottog$workpop_density, main=NULL,
     xlab='density of people in work')

library(corrr)

Correlation <- plottog %>%
  dplyr::select(workpop_density,
                density)%>%
    correlate() %>%
  print()

library(broom)
linearMod <- lm(log(workpop_density) ~ 
                  log(density), 
                data=plottog)

tidy(linearMod)

plottog <- plottog %>%
  mutate(log_density=log(density))%>%
  mutate(log_workpop_density=log(workpop_density))


q <- qplot(x = `log_density`, 
           y = `log_workpop_density`, 
           data=plottog)
q + stat_smooth(method="lm", se=FALSE, size=1) + 
  geom_jitter()

summary(linearMod)

ggplot(plottog, aes(x=log(density), y=log(workpop_density)))+
  geom_point()

model_data <- linearMod %>%
  augment(., plottog)

model_data%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
  geom_histogram()+xlim(-4,4) +xlab('residuals')+ylab('count')

library(olsrr)
ols_plot_resid_qq(linearMod)
ols_test_normality(linearMod)
ols_test_correlation(linearMod)

par(mfrow=c(2,2))
plot(linearMod)


library(car)

boxcox_trans(~workpop_density, 
       plottog)
symbox(~workpop_density, 
       plottog, 
       na.rm=T,
       powers=seq(-3,3,by=.5))
symbox(~density, 
       plottog, 
       na.rm=T,
       powers=seq(-3,3,by=.5))

ggplot(plottog, aes(x=(workpop_density)^-1)) + 
  geom_histogram()
ggplot(plottog, aes(x=log(workpop_density))) + 
  geom_histogram() #better

ggplot(plottog, aes(x=(density)^-1)) + 
  geom_histogram() #better
ggplot(plottog, aes(x=log(density))) + 
  geom_histogram()



b <- boxcox(plottog$density ~ plottog$workpop_density)



```

```{r}


msoabounds <- msoabounds %>%
  mutate(model_final_res = residuals(linearMod))

par(mfrow=c(2,2))
plot(linearMod)

qtm(msoabounds, fill = "model_final_res")
library(spgwr)
msoaboundsSP <- msoabounds %>%
  as(., "Spatial")
coordsmsoaSP <- coordsmsoa %>%
  as(., "Spatial")

GWRbandwidth <- gwr.sel(log(plottog$workpop_density) ~ log(plottog$density),
                  data = msoaboundsSP, 
                        coords=coordsmsoaSP,
                        adapt=T)

#run the gwr model
gwr.model = gwr(log(plottog$workpop_density) ~ log(plottog$density),
                  data = msoaboundsSP, 
                coords=coordsmsoaSP, 
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
gwr.model

gwr.results <- as.data.frame(gwr.model$SDF)
names(gwr.results)

msoaboundsgwr <- msoabounds %>%
  mutate(coefdensity = gwr.results$log.plottog.density.)
tmap_mode('plot')
tm_shape(msoaboundsgwr) +
  tm_borders(lwd=.1)+
  tm_polygons(col = "coefdensity", 
              palette = "RdBu", 
              alpha = 0.5)+

  
  tm_shape(tweets_noisefree_xy) +
  tm_dots(col = "blue")
```

